surfing

### 2021-07-14 inst/surfing.Rmd
document surfing dataset

```{r}
type <- read.table("venuetypes2019.txt",header=TRUE)
type
beachtype <- function(venue){type$beachtype[which(type$comp==venue)]}
beachtype("wct05")
beachtype("wct06")

@@

```{r,label=savesurfiningingdataset}
save(surfing,surfing_maxp,type,surfing_table,file="surfing.rda")
```

>>>>

```{r}
surfing_venuetypes <- read.table("venuetypes2019.txt",header=TRUE)
surfing_venuetypes
beachtype <- function(venue){surfing_venuetypes$beachtype[which(surfing_venuetypes$comp==venue)]}
beachtype("wct05")
beachtype("wct06")

@@

```{r,label=savesurfiningingdataset}
save(surfing,surfing_maxp,surfing_venuetypes,surfing_table,file="surfing.rda")
```
